5D de-aliased seismic data interpolation using non-stationary prediction error filter

### 2021-10-16 npef/paper.tex
Fri Oct 15 21:50:06 CDT 2021
Fri Oct 15 23:05:19 CDT 2021

@@

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_clean5d}
    \label{fig:l_clean5d}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_obs5d}
    \label{fig:l_obs5d}}\\
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_rr5d}
    \label{fig:l_drr5d}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_recon5d}
    \label{fig:l_npef5d}}\\
	\caption{Interpolation results of the noise-free linear-events example for $X=1$ and $Y=1$. (a) Clean data. (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces (S/N=-0.29 dB). (c) Reconstructed data using the rank-reduction method (S/N=30.34 dB). (d) Reconstructed data using the NPEF method (S/N=15.69 dB). }
	\label{fig:l_clean5d,l_obs5d,l_drr5d,l_npef5d}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_clean5d-fk}
    \label{fig:l_clean5d-fk}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_obs5d-fk}
    \label{fig:l_obs5d-fk}}\\
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_rr5d-fk}
    \label{fig:l_drr5d-fk}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_recon5d-fk}
    \label{fig:l_npef5d-fk}}\\
	\caption{\wen{FK spectra of interpolation results of the noise-free linear-events example for $X=1$ and $Y=1$. (a) Clean data. (b) Decimated data. (c) Reconstructed data using the rank-reduction method. (d) Reconstructed data using the NPEF method.} }
	\label{fig:l_clean5d-fk,l_obs5d-fk,l_drr5d-fk,l_npef5d-fk}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s1}
    \label{fig:l_npef1}}
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s2}
    \label{fig:l_npef}}\\
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s3}
    \label{fig:l_npef3}}
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5d_n/Fig/synth_apef5-s4}
    \label{fig:l_npef4}}\\
	\caption{Coefficients cubes of the estimated NPEF for $X=1$ and $Y=1$.  NPEF coefficients corresponding to the first (a), second (b), third (c), and fourth (d) temporal filter indices.   }
	\label{fig:l_npef1,l_npef2,l_npef3,l_npef4}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_clean5d-2}
    \label{fig:l_clean5d2}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_obs5d-2}
    \label{fig:l_obs5d2}}\\
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_rr5d-2}
    \label{fig:l_drr5d2}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/synth_recon5d-2}
    \label{fig:l_npef5d2}}\\
	\caption{Interpolation results of the noise-free linear-events example for $Hx=6$ and $Hy=6$. Each common offset cube has been reshaped into a 2D matrix. (a) Clean data. (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces (S/N=-0.29 dB). (c) Reconstructed data using the rank-reduction method (S/N=30.34 dB). (d) Reconstructed data using the NPEF method (S/N=15.69 dB). }
	\label{fig:l_clean5d2,l_obs5d2,l_drr5d2,l_npef5d2}
\end{figure}

%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_noisy5d}
%    \label{fig:ln_noisy5d}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_obs5d}
%    \label{fig:ln_obs5d}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_rr5d}
%    \label{fig:ln_drr5d}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_recon5d}
%    \label{fig:ln_npef5d}}\\
%	\caption{Interpolation results of the noisy linear-events example for $X=1$ and $Y=1$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Noisy data (S/N=-0.66 dB). (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces (S/N=-0.21 dB). (c) Reconstructed data using the rank-reduction method (S/N=16.83 dB). (d) Reconstructed data using the NPEF method (S/N=2.93 dB). Note that the NPEF method fails in this case.}
%	\label{fig:ln_noisy5d,ln_obs5d,ln_drr5d,ln_npef5d}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_noisy5d-2}
%    \label{fig:ln_noisy5d2}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_obs5d-2}
%    \label{fig:ln_obs5d2}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_rr5d-2}
%    \label{fig:ln_rr5d2}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5d_n/Fig/nsynth_recon5d-2}
%    \label{fig:ln_npef5d2}}\\
%	\caption{Interpolation results of the noisy linear-events example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) Noisy data. (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces. (c) Reconstructed data using the rank-reduction method. (d) Reconstructed data using the NPEF method. Note that the NPEF method fails in this case.}
%	\label{fig:ln_noisy5d2,ln_obs5d2,ln_drr5d2,ln_npef5d2}
%\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_obs5d-3}
    \label{fig:la_obs5d}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_rr5d-3}
    \label{fig:la_drr5d}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_recon5d-3}
    \label{fig:la_npef5d}}\\
	\caption{De-aliased interpolation results of the linear-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the standard rank-reduction method completely fails in this case.}
	\label{fig:la_obs5d,la_drr5d,la_npef5d}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_obs5d-3fk}
    \label{fig:la_obs5dfk}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_rr5d-3fk}
    \label{fig:la_drr5dfk}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/synth_recon5d-3fk}
    \label{fig:la_npef5dfk}}\\
	\caption{\wen{FK spectra of de-aliased interpolation results of the linear-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method.}}
	\label{fig:la_obs5dfk,la_drr5dfk,la_npef5dfk}
\end{figure}

%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_clean5d}
%    \label{fig:h_clean5d}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_obs5d}
%    \label{fig:h_obs5d}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_drr5d}
%    \label{fig:h_drr5d}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{hyper5d/Fig/hyper_recon5d}
%    \label{fig:h_npef5d}}\\
%	\caption{Interpolation results of the noisy hyperbolic-events example for $X=3$ and $Y=3$. (a) Clean data. (b) Irregularly missing data 70\% (S/N=0.59 dB). (c) Reconstructed data using the rank-reduction method (S/N=16.32 dB). (d) Reconstructed data using the NPEF method (S/N=6.38 dB). }
%	\label{fig:h_clean5d,h_obs5d,h_drr5d,h_npef5d}
%\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_obs5d-3}
    \label{fig:ha_obs5d}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_rr5d-3}
    \label{fig:ha_drr5d}}\\
    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_recon5d-3}
    \label{fig:ha_npef5d}}\\
	\caption{De-aliased interpolation results of the hyperbolic-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the standard rank-reduction method completely fails in this case.}
	\label{fig:ha_obs5d,ha_drr5d,ha_npef5d}
\end{figure}

%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_obs5d-3fk}
%    \label{fig:ha_obs5dfk}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_rr5d-3fk}
%    \label{fig:ha_drr5dfk}}\\
%    \subfloat[]{\includegraphics[width=\textwidth]{hyper5da_large/Fig/hyper_recon5d-3fk}
%    \label{fig:ha_npef5dfk}}\\
%	\caption{\wen{FK spectra of de-aliased interpolation results of the hyperbolic-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method.}}
%	\label{fig:ha_obs5dfk,ha_drr5dfk,ha_npef5dfk}
%\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-3-0}
    \label{fig:r_obs5d}}\\
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-3-0}
    \label{fig:r_drr5d}}\\
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-3-0}
    \label{fig:r_npef5d}}\\
	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) The raw data gridded onto regular grids. Those blank areas denote missing traces. (b) Reconstructed data using the damped rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
	\label{fig:r_obs5d,r_drr5d,r_npef5d}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zA}
    \label{fig:r_obs5d1a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zB}
    \label{fig:r_obs5d1b}}\\
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zA}
    \label{fig:r_drr5d1a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zB}
    \label{fig:r_drr5d1b}}\\
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zA}
    \label{fig:r_npef5d1a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zB}
    \label{fig:r_npef5d1b}}\\
	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Note the strong residual noise seen in (f) caused by the NPEF method. }
	\label{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-4-0}
    \label{fig:r_obs5d4}}\\
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-4-0}
    \label{fig:r_drr5d4}}\\
    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-4-0}
    \label{fig:r_npef5d4}}\\
	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) The raw data gridded onto regular grids. Those blank areas denote missing traces. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
	\label{fig:r_obs5d4,r_drr5d4,r_npef5d4}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zA}
    \label{fig:r_obs5d2a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zB}
    \label{fig:r_obs5d2b}}\\
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zA}
    \label{fig:r_drr5d2a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zB}
    \label{fig:r_drr5d2b}}\\
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zA}
    \label{fig:r_npef5d2a}}
    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zB}
    \label{fig:r_npef5d2b}}\\
	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. Note the obviously more discontinuous events in (e) and (f) caused by the NPEF method.}
	\label{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b}
\end{figure}

>>>>

\DeclareRobustCommand{\dlo}[1]{}
\DeclareRobustCommand{\wen}[1]{#1}

\published{Geophysics, 86, no. 5, V419–V429, (2021)}

@@

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_clean5d}
    \label{fig:l_clean5d}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_obs5d}
    \label{fig:l_obs5d}}\\
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_drr5d}
    \label{fig:l_drr5d}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_recon5d}
    \label{fig:l_npef5d}}\\
	\caption{Interpolation results of the noise-free linear-events example for $X=1$ and $Y=1$. (a) Clean data. (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces (S/N=-0.29 dB). (c) Reconstructed data using the rank-reduction method (S/N=30.34 dB). (d) Reconstructed data using the NPEF method (S/N=15.69 dB). }
	\label{fig:l_clean5d,l_obs5d,l_drr5d,l_npef5d}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_clean5d-fk}
    \label{fig:l_clean5d-fk}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_obs5d-fk}
    \label{fig:l_obs5d-fk}}\\
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_drr5d-fk}
    \label{fig:l_drr5d-fk}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_recon5d-fk}
    \label{fig:l_npef5d-fk}}\\
	\caption{\wen{FK spectra of interpolation results of the noise-free linear-events example for $X=1$ and $Y=1$. (a) Clean data. (b) Decimated data. (c) Reconstructed data using the rank-reduction method. (d) Reconstructed data using the NPEF method.} }
	\label{fig:l_clean5d-fk,l_obs5d-fk,l_drr5d-fk,l_npef5d-fk}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5dn/Fig/synth_apef5-s1}
    \label{fig:l_npef1}}
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5dn/Fig/synth_apef5-s2}
    \label{fig:l_npef}}\\
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5dn/Fig/synth_apef5-s3}
    \label{fig:l_npef3}}
    \subfloat[]{\includegraphics[width=0.35\textwidth]{linear5dn/Fig/synth_apef5-s4}
    \label{fig:l_npef4}}\\
	\caption{Coefficients cubes of the estimated NPEF for $X=1$ and $Y=1$.  NPEF coefficients corresponding to the first (a), second (b), third (c), and fourth (d) temporal filter indices.   }
	\label{fig:l_npef1,l_npef2,l_npef3,l_npef4}
\end{figure}

\begin{figure}[htb!]
    \centering
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_clean5d-2}
    \label{fig:l_clean5d2}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_obs5d-2}
    \label{fig:l_obs5d2}}\\
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_drr5d-2}
    \label{fig:l_drr5d2}}
    \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_recon5d-2}
    \label{fig:l_npef5d2}}\\
	\caption{Interpolation results of the noise-free linear-events example for $Hx=6$ and $Hy=6$. Each common offset cube has been reshaped into a 2D matrix. (a) Clean data. (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces (S/N=-0.29 dB). (c) Reconstructed data using the rank-reduction method (S/N=30.34 dB). (d) Reconstructed data using the NPEF method (S/N=15.69 dB). }
	\label{fig:l_clean5d2,l_obs5d2,l_drr5d2,l_npef5d2}
\end{figure}

%% The following was reviewed during revision but actually very informative
%\begin{figure}[htb!]
%   \centering
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_noisy5d}
%   \label{fig:ln_noisy5d}}
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_obs5d}
%   \label{fig:ln_obs5d}}\\
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_drr5d}
%   \label{fig:ln_drr5d}}
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_recon5d}
%   \label{fig:ln_npef5d}}\\
%\caption{Interpolation results of the noisy linear-events example for $X=1$ and $Y=1$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Noisy data (S/N=-0.66 dB). (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces (S/N=-0.21 dB). (c) Reconstructed data using the rank-reduction method (S/N=16.83 dB). (d) Reconstructed data using the NPEF method (S/N=2.93 dB). Note that the NPEF method fails in this case.}
%\label{fig:ln_noisy5d,ln_obs5d,ln_drr5d,ln_npef5d}
%\end{figure}
%
%\begin{figure}[htb!]
%   \centering
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/synth_noisy5d-2}
%   \label{fig:ln_noisy5d2}}
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_obs5d-2}
%   \label{fig:ln_obs5d2}}\\
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_drr5d-2}
%   \label{fig:ln_rr5d2}}
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{linear5dn/Fig/nsynth_recon5d-2}
%   \label{fig:ln_npef5d2}}\\
%\caption{Interpolation results of the noisy linear-events example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) Noisy data. (b) Decimated data \dlo{by}\wen{with} irregularly missing 70\% traces. (c) Reconstructed data using the rank-reduction method. (d) Reconstructed data using the NPEF method. Note that the NPEF method fails in this case.}
%\label{fig:ln_noisy5d2,ln_obs5d2,ln_drr5d2,ln_npef5d2}
%\end{figure}
%% The above was reviewed during revision but actually very informative

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_obs5d-3}
   \label{fig:la_obs5d}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_drr5d-3}
   \label{fig:la_drr5d}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_recon5d-3}
   \label{fig:la_npef5d}}\\
\caption{De-aliased interpolation results of the linear-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the standard rank-reduction method completely fails in this case.}
\label{fig:la_obs5d,la_drr5d,la_npef5d}
\end{figure}

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_obs5d-3fk}
   \label{fig:la_obs5dfk}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_drr5d-3fk}
   \label{fig:la_drr5dfk}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{linear5da/Fig/la_recon5d-3fk}
   \label{fig:la_npef5dfk}}\\
\caption{\wen{FK spectra of de-aliased interpolation results of the linear-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method.}}
\label{fig:la_obs5dfk,la_drr5dfk,la_npef5dfk}
\end{figure}

\begin{figure}[htb!]
   \centering
   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_obs5d-3}
   \label{fig:ha_obs5d}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_rr5d-3}
   \label{fig:ha_drr5d}}\\
   \subfloat[]{\includegraphics[width=\textwidth]{hyper5da/Fig/ha_recon5d-3}
   \label{fig:ha_npef5d}}\\
\caption{De-aliased interpolation results of the hyperbolic-events example for $X=3$ and $Y=3$. Each common midpoint cube has bee reshaped into a 2D matrix. (a) Regularly missing data. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the standard rank-reduction method completely fails in this case.}
\label{fig:ha_obs5d,ha_drr5d,ha_npef5d}
\end{figure}

%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-3-0}
%    \label{fig:r_obs5d}}\\
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-3-0}
%    \label{fig:r_drr5d}}\\
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-3-0}
%    \label{fig:r_npef5d}}\\
%	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) The raw data gridded onto regular grids. Those blank areas denote missing traces. (b) Reconstructed data using the damped rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
%	\label{fig:r_obs5d,r_drr5d,r_npef5d}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zA}
%    \label{fig:r_obs5d1a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cog-zB}
%    \label{fig:r_obs5d1b}}\\
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zA}
%    \label{fig:r_drr5d1a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cog-zB}
%    \label{fig:r_drr5d1b}}\\
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zA}
%    \label{fig:r_npef5d1a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cog-zB}
%    \label{fig:r_npef5d1b}}\\
%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d,r_drr5d,r_npef5d}. Note the strong residual noise seen in (f) caused by the NPEF method. }
%	\label{fig:r_obs5d1a,r_obs5d1b,r_drr5d1a,r_drr5d1b,r_npef5d1a,r_npef5d1b}
%\end{figure}
%
%
%
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_obs5d-4-0}
%    \label{fig:r_obs5d4}}\\
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_drr5d-4-0}
%    \label{fig:r_drr5d4}}\\
%    \subfloat[]{\includegraphics[width=0.9\textwidth]{real5d_smaller/Fig/real_npef5d-4-0}
%    \label{fig:r_npef5d4}}\\
%	\caption{Interpolation results of a real 5D seismic data example for $Hx=6$ and $Hy=6$. Each common offset cube has bee reshaped into a 2D matrix. (a) The raw data gridded onto regular grids. Those blank areas denote missing traces. (b) Reconstructed data using the rank-reduction method. (c) Reconstructed data using the NPEF method. Note that the damped rank-reduction outperforms the NPEF method in the case of irregularly missing traces.}
%	\label{fig:r_obs5d4,r_drr5d4,r_npef5d4}
%\end{figure}
%
%
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zA}
%    \label{fig:r_obs5d2a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_obs5d-cmg-zB}
%    \label{fig:r_obs5d2b}}\\
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zA}
%    \label{fig:r_drr5d2a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_drr5d-cmg-zB}
%    \label{fig:r_drr5d2b}}\\
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zA}
%    \label{fig:r_npef5d2a}}
%    \subfloat[]{\includegraphics[width=0.4\textwidth]{real5d_smaller/Fig/real_npef5d-cmg-zB}
%    \label{fig:r_npef5d2b}}\\
%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:r_obs5d4,r_drr5d4,r_npef5d4}. Note the obviously more discontinuous events in (e) and (f) caused by the NPEF method.}
%	\label{fig:r_obs5d2a,r_obs5d2b,r_drr5d2a,r_drr5d2b,r_npef5d2a,r_npef5d2b}
%\end{figure}
%
%
%\begin{figure}[htb!]
%    \centering
%   \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
%%    \subfloat[]{\includegraphics[width=1.0\textwidth]{Fig/test2} %eps2pdf problem
%    \label{fig:ra_obs5d}}\\
%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3-0}
%    \label{fig:ra_npef5d}}\\
%	\caption{De-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$. We treat the reconstructed data using the damped rank-reduction method as the starting data and further interpolate a trace every other traces in the $X$ and $Y$ directions. Each common offset cube has bee reshaped into a 2D matrix. (a) The regularly sampled data. Those blank areas denote missing traces. (b) Reconstructed data using the NPEF method. In this case of regularly missing traces, the rank-reduction method completely fails so we omit its result.}
%	\label{fig:ra_obs5d,ra_npef5d}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3-0}
%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_obs5d_new-3fk} %eps2pdf problem
%    \label{fig:ra_obs5d_new-3fk}}\\
%    \subfloat[]{\includegraphics[width=1.0\textwidth]{real5d_smaller/Fig/real_npef5d_new-3fk}
%    \label{fig:ra_npef5d_new-3fk}}\\
%	\caption{\wen{FK spectra of de-aliased interpolation results of the real 5D seismic data example for $Hx=6$ and $Hy=6$. (a) The regularly sampled data before interpolation. (b) Reconstructed data using the NPEF method. }}
%	\label{fig:ra_obs5d_new-3fk,ra_npef5d_new-3fk}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zA}
%    \label{fig:r_obs5da}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_obs5d_new-cog-zB}
%    \label{fig:r_npef5db}}\\
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zA}
%    \label{fig:r_obs5da}}
%    \subfloat[]{\includegraphics[width=0.45\textwidth]{real5d_smaller/Fig/real_npef5d_new-cog-zB}
%    \label{fig:r_npef5db}}\\
%	\caption{Left column: zoomed comparison of frame boxes A in Figure \ref{fig:ra_obs5d,ra_npef5d}. Right column: zoomed comparison of frame boxes B in Figure \ref{fig:ra_obs5d,ra_npef5d}.}
%	\label{fig:ra_obs5da,ra_npef5da,ra_obs5db,ra_npef5db}
%\end{figure}
%
%\begin{figure}[htb!]
%    \centering
%    \subfloat[]{\includegraphics[width=\textwidth]{real5d_smaller_onestep/Fig/os_obs}
